---
title: "Untitled"
author: "ATR"
date: "2023-08-01"
output: html_document
---

```{r}
library(sf)
library(tigris)
library(tidyverse)
library(lme4)
library(mgcv)
#library(itsadug)
#library(reghelper)
library(caret)
library(parallel)
library(dplyr)
library(stringr)
library(ggplot2)
library(ggpubr)
library(readr)
```

```{r}
corn_data <- read_rds('data/AFT-data/corn_all_data_n15_om10_AFT.rds')
soy_data <- read_rds('data/AFT-data/soy_all_data_n15_om10_AFT.rds')
wheat_data <- read_rds('data/AFT-data/wheat_all_data_n15_om10_AFT.rds')
```


```{r}

write.csv(corn_data, 'data/AFT-data/corn_all_data_n15_om10_AFT.csv')
write.csv(soy_data, 'data/AFT-data/soy_all_data_n15_om10_AFT.csv')
write.csv(wheat_data, 'data/AFT-data/wheat_all_data_n15_om10_AFT.csv')

```


```{r}
corn_counties <- corn_data %>% select(GEOID) %>% unique()
soy_counties <- soy_data %>% select(GEOID) %>% unique()
wheat_counties <- soy_data %>% select(GEOID) %>% unique()
```

#Adding a corn, soy, and wheat colums to help distinguish the yield data, selecting GEOID
```{r}
corn_counties <- corn_data %>% select(GEOID) %>% unique() %>% mutate(corn = 'corn')

soy_counties <- soy_data %>% select(GEOID) %>% unique() %>% mutate(soy = 'soy')

wheat_counties <- wheat_data %>% select(GEOID) %>% unique() %>% mutate(wheat = 'wheat')

corn_soy_counties <- full_join(corn_counties, soy_counties, by="GEOID")

```
`
#Adding a corn, soy, and wheat colums to help distinguish the yield data, selecting GEOID and year
```{r}
corn_data_2 <- corn_data %>% select(c("GEOID", "year"))%>% mutate(corn = 'corn')

soy_data_2 <- soy_data %>% select(c("GEOID", "year")) %>% mutate(soy = 'soy')

wheat_data_2 <- wheat_data %>% select(c("GEOID", "year")) %>% mutate(wheat = 'wheat')

```

#Adding a corn, soy, and wheat colums to help distinguish the yield data, selecting GEOID and year, state-alpha, county_name, and irrigation status. This is the one we use 
```{r}
corn_data_3 <- corn_data %>% select(c("GEOID", "year", "state_alpha", "county_name", "Yield_mg_ha",  "irrigated"))%>% mutate(corn = 'corn')

soy_data_3 <- soy_data %>% select(c("GEOID", "year", "state_alpha", "county_name", "Yield_mg_ha", "irrigated")) %>% mutate(soy = 'soy')

wheat_data_3 <- wheat_data %>% select(c("GEOID", "year", "state_alpha", "county_name", "Yield_mg_ha", "irrigated")) %>% mutate(wheat = 'wheat')

corn_soy_data3 <- full_join(corn_data_3, soy_data_3, by= c("GEOID", "year", "state_alpha", "county_name", "irrigated"))

all_data3 <- full_join(corn_soy_data3, wheat_data_3, by= c("GEOID", "year", "state_alpha", "county_name", "irrigated"))
head(all_data3)
```

#Checking for the presence of wheat. It all checks out. 
```{r}
wheat <- subset(all_data3, wheat=="wheat")
```

#Save file as a .csv  to be uploaded in GIS 
```{r}
write.csv(all_data3, 'data/AFT-data/corn_soy_wheat.csv')
```

